MetaTracts - A Method for Robust Extraction and Visualization of Carbon Fiber Bundles in Fiber Reinforced Composites

### 2014-09-18 chapters/MetaTracts.tex
updating images
Updated with Artem's images
revise update
revise update
Minor local commit
Minor local commit
local commit
Added new images

\begin{figure}[tb]
\centering
%\includegraphics[width=0.45\textwidth]{imagesMT2014/MT_data_4_2.png}
\includegraphics[width=0.5\textwidth]{imagesMT2014/image1}
\caption{Data Characteristics. (A) shows a rendering of the data. (B) shows 2D slices along the X and (C) along the Z axis. (D) close up of the region marked in green in (C), multiple fiber bundles cross and are indistinguishable by visual inspection alone. }
\label{fig:data-char}
\end{figure}
\section {Data Characteristic and Assumptions}
\label{sec:char_data}

@@

%
\begin{figure}[tb]
\centering
%\includegraphics[width=0.45\textwidth]{imagesMT2014/MT_data_rh.png}
\includegraphics[width=0.5\textwidth]{imagesMT2014/image2}
\caption{Reliable Hessians. (A) Colored according to Orientation vector mapped to RGB. (B) 2D slice along Z and (C) along X axis. (D) close up of the region marked in green in C.}
\label{fig:reliable_hessian}
\end{figure}

@@

\begin{figure}[tb]
  \centering  	
 %\includegraphics[width=0.45\textwidth]{imagesMT2014/crop-16/orientation_cluster.PNG}
  \includegraphics[width=0.55\textwidth]{imagesMT2014/garb2}
  	\caption{(B) Result of K means clustering with data points projected to the top three eigenvectors as major axes. (A) MetaTracts belonging to orientation cluster 1. (B) MetaTracts belonging to orientation cluster 2. MetaTracts in gray(A,C) show context. }
  \label{fig:orientation_clustering}
  \end{figure}

@@

The directed Hausdorff distance is very sensitive to outliers in the data.
However, because MetaTracts after orientation clustering are constructed using cylinders with similar orientations, they are not plagued by outliers.
To cluster based on MetaTract proximity, we used single linkage hierarchical clustering.
Hierarchical clustering has a single parameter $h$, the desired number of clusters.
In hierarchical clustering each objects starts in its own cluster and clusters are merged based on some criterion.
Clusters are merged until there are only $h$ clusters left.
Hierarchical clustering is intuitive since it is easy to trace how clusters are formed and merged.
Single linkage clustering finds pairs of objects $p \in P$ and $q \in Q$ where $P \neq Q$ which are closer than other such pairs, and merges the containing clusters $P$ and $Q$.
We found that single linkage hierarchical clustering had two major drawbacks.
First, the clustering would produce some small clusters of just a few MetaTracts.
These MetaTracts were anomalies caused by noise in the data and did not represent true fiber bundles.
Second, if two fiber bundles were parallel for some of their length and then separated, they would sometimes be clustered into the same fiber bundle.
A short MetaTract which was parallel to both and did not extend into the separation region could form a link between the two fiber bundles, causing them to be clustered into a single bundle.
To address the problem of small clusters, we applied hierarchical clustering and then identified small clusters with few MetaTracts.
We removed the MetaTracts that were in those clusters from the data set and reapplied hierarchical clustering.
To address the problem of short MetaTracts joining different fiber bundles, we applied hierarchical clustering and then removed the
shortest fibers (fibers less than 0.6 times the median length) in each bundle. We then reapplied hierarchical clustering.
We repeated both until a steady state of clusters is reached and no new small fibers can be removed. The results of clustering the orientation clusters Fig.~\ref{fig:orientation_clustering}(A,C) are shown in Fig.~\ref{fig:orientation_clustering}(D,E) respectively. Note how the purple cluster Fig.~\ref{fig:orientation_clustering}(E) bundle ``7'' is extracted well.
\begin{figure}
\centering
		%\includegraphics[width=0.4\textwidth]{imagesMT2014/garb1}~
		\includegraphics[width=0.5\textwidth]{imagesMT2014/image7b}
	%\includegraphics[width=0.45\textwidth]{imagesMT2014/crop-16/bundles}~ 
	%\includegraphics[height=0.35\textwidth]{imagesMT2014/crop-16/vol_mesh.png} 
	\caption{(A) Volume rendering of data set Figure~\ref{fig:data-char}A.(B) shows a single slice of the data set. (C) shows two of the extracted meshes together. (D) shows the meshes separately.}
	\label{fig:crop-16-decomp}
\end{figure}

@@

\begin{figure}[t]
\centering
	\includegraphics[width=0.45\textwidth]{imagesMT2014/image8.PNG}
	\caption{Data set with flat thin and compact bundles. (A) shows the volume rendering and a 2D slice with one of the boundaries marked in green, (B) shows the clusters according to individual orientation. (C) shows the complete result. (D) shows the voxelization of (C).}
	\label{fig:prepreg}
\end{figure}

>>>>

\begin{figure}[tb]
\centering
%\includegraphics[width=0.45\textwidth]{imagesMT2014/MT_data_4_2.png}
\includegraphics[width=0.5\textwidth, trim = 0mm 110mm 0mm 0mm, clip,]{imagesMT2014/image1B.pdf}
\caption{Data Characteristics. (A) shows a rendering of the data. (B) shows 2D slices along the X and (C) along the Z axis. (D) close up of the region marked in green in (C), multiple fiber bundles cross and are indistinguishable by visual inspection alone. }
\label{fig:data-char}
\end{figure}
\section {Data Characteristic and Assumptions}
\label{sec:char_data}

@@

%
\begin{figure}[tb]
\centering
%\includegraphics[width=0.45\textwidth]{imagesMT2014/MT_data_rh.png}
\includegraphics[width=0.5\textwidth,  trim = 0mm 90mm 0mm 0mm, clip]{imagesMT2014/image2B.pdf}
\caption{Reliable Hessians. (A) Colored according to Orientation vector mapped to RGB. (B) 2D slice along Z and (C) along X axis. (D) close up of the region marked in green in C.}
\label{fig:reliable_hessian}
\end{figure}

@@

\begin{figure}[tb] 
  \centering  	
 %\includegraphics[width=0.45\textwidth]{imagesMT2014/crop-16/orientation_cluster.PNG}
 \includegraphics[width=0.5\textwidth]{imagesMT2014/image_clustering.png}
  	\caption{(B) Result of K means clustering with data points projected to the top three eigenvectors as major axes. (A) MetaTracts belonging to orientation cluster 1. (C) MetaTracts belonging to orientation cluster 2. MetaTracts in gray(A,C) show context.
  	(D,E) shows the result of distance based clustering on the orientation cluster. (F) shows the combined result. }
  \label{fig:orientation_clustering}
  \end{figure}

@@

The directed Hausdorff distance is very sensitive to outliers in the data.
However, because MetaTracts after orientation clustering are constructed using cylinders with similar orientations, they are not plagued by outliers.
To cluster based on MetaTract proximity, we used single linkage hierarchical clustering.
Hierarchical clustering has a single parameter $h$, the desired number of clusters.
In hierarchical clustering each objects starts in its own cluster and clusters are merged based on some criterion.
Clusters are merged until there are only $h$ clusters left.
Hierarchical clustering is intuitive since it is easy to trace how clusters are formed and merged.
Single linkage clustering finds pairs of objects $p \in P$ and $q \in Q$ where $P \neq Q$ which are closer than other such pairs, and merges the containing clusters $P$ and $Q$.
We found that single linkage hierarchical clustering had two major drawbacks.
First, the clustering would produce some small clusters of just a few MetaTracts.
These MetaTracts were anomalies caused by noise in the data and did not represent true fiber bundles.
Second, if two fiber bundles were parallel for some of their length and then separated, they would sometimes be clustered into the same fiber bundle.
A short MetaTract which was parallel to both and did not extend into the separation region could form a link between the two fiber bundles, causing them to be clustered into a single bundle.
To address the problem of small clusters, we applied hierarchical clustering and then identified small clusters with few MetaTracts.
We removed the MetaTracts that were in those clusters from the data set and reapplied hierarchical clustering.
To address the problem of short MetaTracts joining different fiber bundles, we applied hierarchical clustering and then removed the
shortest fibers (fibers less than 0.6 times the median length) in each bundle. We then reapplied hierarchical clustering.
We repeated both until a steady state of clusters is reached and no new small fibers can be removed. The results of clustering the orientation clusters Fig.~\ref{fig:orientation_clustering}(A,C) are shown in Fig.~\ref{fig:orientation_clustering}(D,E) respectively. Note how the purple cluster Fig.~\ref{fig:orientation_clustering}(E) bundle ``7'' is extracted well.
\begin{figure}
\centering
		%\includegraphics[width=0.4\textwidth]{imagesMT2014/garb1}~
		\includegraphics[width=0.5\textwidth, trim = 0mm 70mm 0mm 15mm, clip]{imagesMT2014/image7b.pdf}
	%\includegraphics[width=0.45\textwidth]{imagesMT2014/crop-16/bundles}~ 
	%\includegraphics[height=0.35\textwidth]{imagesMT2014/crop-16/vol_mesh.png} 
	\caption{(A) Volume rendering of data set Figure~\ref{fig:data-char}A.(B) shows a single slice of the data set. (C) shows two of the extracted meshes together. (D) shows the meshes separately.}
	\label{fig:crop-16-decomp}
\end{figure}

@@

\begin{figure}[t]
\centering
%	\includegraphics[width=0.45\textwidth]{imagesMT2014/image8b}
	\caption{Data set with flat thin and compact bundles. (A) shows the volume rendering and a 2D slice with one of the boundaries marked in green, (B) shows the clusters according to individual orientation. (C) shows the complete result. (D) shows the voxelization of (C).}
	\label{fig:prepreg}
\end{figure}
